Space transformation in Multidimensional IRT (Lemmas)

### 2022-08-05 notebooks/Space_transformation_theorem.qmd
The intermediate steps are basic algebra results and can be left implicit without further consideration.

Therefore, $`r DIR_COS_VEC_EQ2`$ and $`r TRAIT_VECTOR_POLAR_EQ2`$.[^9]
$\blacksquare$
:::
:::

@@

[^9]: I don't quite understand the whole proof, particularly, the equivalence
    $`r latex_eq(latex(latex_transp(STD_BASIS_VECTOR_ANY), INNER_PROD_MATRIX), INNER_PROD_MATRIX_ROW)`$,
    and the step from $`r DIR_COS_ANY`$ to $`r DIR_COS_VEC`$. This step is
    similar to my step from Equation 6 to Equation 7 in the draft, which I had
    the feeling was missing some intermediate steps.

>>>>

Therefore, $`r DIR_COS_VEC_EQ2`$ and $`r TRAIT_VECTOR_POLAR_EQ2`$.
$\blacksquare$
:::
:::

@@
